---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pederlib

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![CRAN status](https://www.r-pkg.org/badges/version/pederlib)](https://CRAN.R-project.org/package=pederlib)

<!-- badges: end -->

The goal of pederlib is to ...

## Installation

You can install the development version of pederlib from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pedersebastian/pederlib")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(pederlib)
## basic example code
```

| Function                        | Name              | Description |
|---------------------------------|-------------------|-------------|
| Control race with new delfaults | ctrl(...)         |             |
| Dates                           | dates()           |             |
| Geometric mean of sens and spec | g_mean            |             |
| juice                           | juice()           |             |
| Komma                           | komma(...)        |             |
| Mode                            | mode_vec(x)       |             |
| Metric set                      | mset()            |             |
| Percent                         | pct()             |             |
| Prosent                         | prosent()         |             |
| Read CSV Europe                 | read_csv_europe() |             |
| Sitemap                         | sitemap()         |             |
| Startup                         | startup()         |             |
| Sum fun                         | sum_fun()         |             |
| Theme Center                    | theme_center()    |             |
| Theme Pedr                      | theme_pedr()      |             |
| Use split                       | use_split()       |             |
| ##autoplot workflowset          |                   |             |
