---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pederlib

<!-- badges: start -->

<!-- badges: end -->

## Installation

You can install the development version of pederlib from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pedersebastian/pederlib")
```

## Example


```{r example}
library(pederlib)

```

| Add on to  | Function name     | Description                                                                                                                                        |
|------------|-------------------|----------------------------------------------------------------------------------------------------------------------------------------------------|
| ggplot2    | theme_center()    | Based on theme_minimal(), except light gray for background for the title of facets, and all titles are centered                                    |
|            | theme_pedr()      | Font: BentonSans, used in eg. Sykepleien forskning. Otherwise like theme_center()                                                                  |
| scales     | komma()           | like scales::comma_format(), only that the decimal mark is "," - not "."                                                                           |
|            | prosent           | ike scales::percent_format(), only that the decimal mark is "," - not "."                                                                          |
| yardstick  | rmsle()           | Root mean squared log error for yardstick                                                                                                          |
|            | g_mean()          | Geometric mean of sensitivity and specificity                                                                                                      |
|            | mset()            | return a metric_set object with different types of metric for regression and classification                                                        |
|            |                   |                                                                                                                                                    |
| "original" | read_csv_europe() | import csv using European encoding ("CP1252"), uses the vroom-package                                                                              |
|            | mode()            | find the mode from a vector                                                                                                                        |
|            | sum_fun()         | Summarize function, returns a tibble                                                                                                               |
|            | use_split()       | Like the package usemodels, this function returns standard for spiting data into testing and training. Also create re samples from the testing-set |


